BIOL 274 Homework 1

### 2024-01-24 bio_dynamics/bio274_hw1.Rmd
revised hw1 based on class lecture

@@

$$y^{-\frac{1}{3}} \, dy=x \, dx$$
$$\int y^{-\frac{1}{3}} \, dy= \int x \, dx$$
$$\frac{3}{2}y^{\frac{2}{3}}=\frac{x^2}{2}+C_1$$
$$y^{\frac{2}{3}}=\frac{x^2+C_2}{3}$$
$$y=\left(\frac{x^2+C_2}{3} \right)^\frac{3}{2}=\frac{(x^2+C_2)^{\frac{3}{2}}}{3\sqrt3}$$

@@

$$\frac{dT}{dt}=k(T_{body}-T_{env})=k(T_{body}-20)$$
$$
\frac{1}{(T_{body}-20)}dT=k\,dt
$$
$$\int\frac{1}{(T_{body}-20)}dT=kt+C$$

$$\ln{(T_{body}-20)}=kt+C$$
$$T_{body}=e^{kt+C}+20=Ce^{kt}+20$$

Since $T_{body}=C+20$ at time $t=0$, we can write the equation as
$$T_{body}(t)=(T_0-20)e^{kt}+20$$
for the temperature of the body at time $t$.
Now using the information we are given,
$$60=(100-20)e^{10k}+20$$
$$40=80e^{10k}$$
$$\frac{1}{2}=e^{10k}$$
$$\frac{\ln{(1/2)}}{10}=k$$

@@

$$\frac{1}{x}dx=-t\,dt$$
$$\int \frac{1}{x}dx=\int-t\,dt$$
$$\ln{(x)}=-\frac{t^2}{2}+C$$

$$x(t)=Ce^{-t^2/2}$$
is our general solution to the differential equation.
Now we plug in the initial conditions:
$$1/\sqrt{\pi}=Ce^{-(0^2/2)}=Ce^0=C$$

$$x(t)=\frac{e^{-t^2/2}}{\pi}$$

@@

$$ \frac{u^3}{3}=\frac{1}{9}\sin(t)+C$$

$$ u^3=\frac{\sin(t)}{3}+C$$

Now we plug in the initial conditions:
$$ 2^3=\frac{\sin(0)}{3}+C=0+C$$
So $C=8$ and we have
$$ u(t)=\sqrt[3]{\frac{\sin(t)}{3}+8}$$

>>>>

We can see that $\frac{dP}{dt}$ is indeed positive and negative over the expected intervals.

@@

$$y^{-\frac{1}{3}} \, dy=x \, dx$$
$$\int y^{-\frac{1}{3}} \, dy= \int x \, dx$$
$$\frac{3}{2}y^{\frac{2}{3}}=\frac{x^2}{2}+C_1$$
$$y^{\frac{2}{3}}=\frac{x^2+C_2}{3}$$
$$y(x)=\left(\frac{x^2+C_2}{3} \right)^\frac{3}{2}=\frac{(x^2+C_2)^{\frac{3}{2}}}{3\sqrt3}$$
Note that $y(x)=0$ is also a solution to the ODE, because $\frac{dy}{dx}$ will equal 0 for all $x$ and $x\sqrt[3]{0}=0$.

@@

$$\frac{dT}{dt}=k(T_{body}-T_{env})=k(T_{body}-20)$$
$$
\frac{1}{(T_{body}-20)}dT=k\,dt
$$
$$\int\frac{1}{(T_{body}-20)}dT=\int k\,dt$$
$$\ln{(T_{body}-20)}=kt+C_1$$
$$T_{body}=e^{kt+C_1}+20=C_2e^{kt}+20$$
where $C_2=e^{C_1}$.

Since $T_{body}=C_2+20$ at time $t=0$, we can write the equation as
$$T_{body}(t)=(T_0-20)e^{kt}+20$$
for the temperature of the body at time $t$.
Now using the information we are given,
$$60=(100-20)e^{10k}+20$$
$$40=80e^{10k}$$
$$\frac{1}{2}=e^{10k}$$
$$\frac{\ln{(1/2)}}{10}=k$$

@@

$$\frac{1}{x}dx=-t\,dt$$
$$\int \frac{1}{x}dx=\int-t\,dt$$
$$\ln{(x)}=-\frac{t^2}{2}+C_1$$

$$x(t)=C_2e^{-t^2/2}$$
is our general solution to the differential equation, where $C_2=e^{C_1}$.
Now we plug in the initial conditions:
$$1/\sqrt{\pi}=C_2e^{-(0^2/2)}=C_2e^0=C_2$$

$$x(t)=\frac{e^{-t^2/2}}{\sqrt{\pi}}$$

@@

$$ \frac{u^3}{3}=\frac{1}{9}\sin(t)+C_1$$

$$ u^3=\frac{\sin(t)}{3}+C_2$$

Where $C_2=3C_1$.
Now we plug in the initial conditions:
$$ 2^3=\frac{\sin(0)}{3}+C_2=0+C_2$$
So $C_2=8$ and we have
$$ u(t)=\sqrt[3]{\frac{\sin(t)}{3}+8}$$
